The K2 Halo Photometry Campaign

### 2019-04-01 paper/ms.tex
typo
tess ninja 2 acknowledgement
figure included

\noindent The weights are chosen to minimize the a modified Total Variation

@@

@@

>>>>

\noindent The weights are chosen to minimize the modified Total Variation

@@

\begin{figure*}
\plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.png}
\end{figure*}

@@

This project was developed in part at the Building Early Science with TESS meeting, which took place in March 2019 at the University of Chicago.
